% Acknowledgements (Acceptable American spelling) are optional
% So are Acknowledgments (proper English spelling)
    \chapter*{Acknowledgements}
	There are a variety of people who have made this thesis possible. I'd like to start by thanking Daniel Borrero, who advised me this year. Along the way he also showed me the bouncing droplet system, helped me troubleshoot experimental issues, showed me reason, logic, corrected endless drafts, introduced me to John Bush (that's right; John Bush \rf{pilot-wave}), and a bunch of other things. Thanks Daniel, for being so generous with your time and energy. I'm also greatly indebted to Jay for help with the design and construction of various components of the thesis, and for always having a great attitude. Noah and Bob were also gracious enough to lend me equipment and help overcome a few technical obstacles. Finally, thanks to Lily, Kai, and Jack for reading over my drafts.
	
	More broadly, I owe a lot of my growth, both personal and academic, to a couple of excellent professors at Reed. Most of my physics education can be traced to Daniel, Darrell, Nelia, johnny, Lucas, Joel, and everyone else in the department. I learned a lot about hard work, lab skills, and physics. In other disciplines, I've had the pleasure of learning from Libby, Albert, Alan, and others who introduced me their subjects and helped me as I stumbled along. 
	
	Finally, I'd like to thank all of the people who supported me during my time at Reed. Thanks to Mom and Dad for basically everything. Kai, thanks for being my friend for 4 years, I couldn't have done it without you. You are the best $\beta$ a guy could wish for. In all seriousness though, I love you. Finally, I have to thank Lily and Clops. They, notably Clops, have been incredibly supportive of everything I have done for the last two and half years. 

	
	